---
title: ""
author: ""
date: "2023-06-21"
output: pdf_document
---

\fontfamily{lmss}
\fontsize{10}{10}
\selectfont

__AgTech Product Name Generator (Exploratory Design)__

MJB - 2023-06-21

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringi)
```

\tableofcontents

---

Stipulations: 

* Approx. 3 syllables
* Model the form "ceria"
* Try the suffix "-bact"
* Product lists a person can read through but not overwhelm

A person can peruse the lists and maybe find the right *de novo* product name, but they could also simply be inspired to come up with good names that the market and customers would enjoy. 

Each time this script is run, it takes a couple seconds and generates all-new lists (in PDF form). This is amenable to revision and refining to get generations of name/brand ideas closer to what would be the most appropriate product names for AgTech products. 

\newpage

### consonant+vowel+consonant+vowel+consonant+vowel

This should generate 3-syllable words of the simplest "consonant+vowel" form. We'll make 900 iterations, which is on the low-end of possibilities, and then bump it up to bigger numbers later when we find the sweet spot. 

```{r}
sprintf("%s%s%s%s%s%s", 
        stri_rand_strings(900, 1, '[BCDFGHJKLMNPQRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHJKLMNPQRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHJKLMNPQRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'))
```

\newpage

### vowel+consonant+vowel+consonant+vowel+consonant

Now we can generate 3-syllable words of the other simplest form "vowel+consonant". 

```{r}
sprintf("%s%s%s%s%s%s", 
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHJKLMNPQRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHJKLMNPQRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHJKLMNPQRSTVWXYZ]'))
```

\newpage

\newpage

### vowel+consonant+vowel+consonant+vowel

Now let's generate 3-syllable words of the other simplest form "vowel+consonant" again but leave off the consonant on the end. 

```{r}
sprintf("%s%s%s%s%s", 
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHJKLMNPQRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHJKLMNPQRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'))
```

\newpage

### consonant+vowel+consonant+consonant+vowel+vowel

Let's get a little freaky and limit the consonants and vowels a little to get closer to what we might want at each letter. 

```{r}
sprintf("%s%s%s%s%s%s", 
        stri_rand_strings(900, 1, '[CDGHJKLMNPRSTVWZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHKLMNPRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[BCDFGHKLMNPRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[AEO]'),
        stri_rand_strings(900, 1, '[AEO]'))
```


\newpage

### consonant+vowel+consonant+consonant+I+A

What if we just use "IA" at the end of the previous word form? 

```{r}
sprintf("%s%s%s%s%s%s", 
        stri_rand_strings(900, 1, '[CDGHJKLMNPRSTVWZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHKLMNPRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[BCDFGHKLMNPRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[I]'),
        stri_rand_strings(900, 1, '[A]'))
```

\newpage

### consonant+vowel+consonant+consonant+B+A+C+T

Let's add "BACT" to the end of C+A+C+A words and see what happens. 

```{r}
sprintf("%s%s%s%s%s%s%s%s", 
        stri_rand_strings(900, 1, '[CDGHJKLMNPRSTVWZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[BCDFGHKLMNPRSTVWXYZ]'),
        stri_rand_strings(900, 1, '[AEIOU]'),
        stri_rand_strings(900, 1, '[B]'),
        stri_rand_strings(900, 1, '[A]'),
        stri_rand_strings(900, 1, '[C]'),
        stri_rand_strings(900, 1, '[T]'))
```

